\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-10 NAR_DRAFT.tex
edits
figure 2 caption

\subsection{Real Data}
We analyzed two real data sets, one from an acute myeloid leukemia, and one from a multi-region sequencing experiment in breast cancer \cite{Griffith2015,Shi2018}.
We downloaded the normal and primary tumor bam files generated for the whole genome sequences in \citet{Griffith2015} from dbGaP accession number phs000159.v8.p4.
\citet{Griffith2015} generated a platinum set of variant calls for this primary tumor, which we obtained from supplementary materials, and used for our true positive dataset.
The whole exome sequencing bam files generated by \citet{Shi2018} were downloaded from NCBI SRA no. SRP070662.
\citet{Shi2018} generated a gold set of variant calls for each tumor region sequenced, which we obtained from supplementary materials and used for our true positive dataset.
We called variants using Mutect 1.1.7 with the same parameters as described above, except that both of these data sets were originally aligned to GRCH37, and we used that reference here.

@@

  \begin{figure*}
    \begin{center}
    \includegraphics{figures/fig_wes.pdf}
    \end{center}
    \caption{Model performance on 500X simulated whole exome.
    \textbf{(a)} Precision recall curves and \textbf{(c)} Receiver operating characteristic curves for 3 mutation signatures.
    Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the \batcave model.
    A perfectly calibrated model would generate the diagonal line.}
  \label{NAR-wes_fig}
  \end{figure*}

>>>>

\subsection{Real Data}
We analyzed two real data sets, one from an acute myeloid leukemia, and one from a multi-region sequencing experiment in breast cancer \cite{Griffith2015,Shi2018}.
We downloaded the normal and primary tumor bam files generated for the whole genome sequences in \citet{Griffith2015} from dbGaP accession number phs000159.v8.p4.
\citet{Griffith2015} generated a platinum set of variant calls for this primary tumor, which we obtained from supplementary materials, and used for our true positive dataset.
The whole exome sequencing bam files generated by \citep{Shi2018} were downloaded from NCBI SRA no. SRP070662.
\citet{Shi2018} generated a gold set of variant calls for each tumor region sequenced, which we obtained from supplementary materials and used for our true positive dataset.
We called variants using Mutect 1.1.7 with the same parameters as described above, except that both of these data sets were originally aligned to GRCH37, and we used that reference here.

@@

  \begin{figure*}
    \begin{center}
    \includegraphics{figures/fig_wes.pdf}
    \end{center}
    \caption{Model performance.
    \textbf{(a)} Precision-recall curves and \textbf{(b)} Receiver operating characteristic curves for 3 mutation signatures.
    Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{(c)} the MuTect model and \textbf{(d))} the \batcave model.
    A perfectly calibrated model would generate the diagonal line. Precision-recall curves for real data \textbf{(e)} and \textbf{(f)}}
  \label{NAR-wes_fig}
  \end{figure*}
